Explore the SingleR results

### 2025-07-17 analyses/cell-type-neuroblastoma-04/exploratory-notebooks/singler-results.Rmd

# Define color ramp for shared use in the heatmaps
heatmap_col_fun <- circlize::colorRamp2(c(0, 1), colors = c("white", "darkslateblue"))
# Set heatmap padding option
ComplexHeatmap::ht_opt(TITLE_PADDING = grid::unit(0.6, "in"))
```

@@

# merged SCE file
sce_file <- file.path(
  data_dir,
  "SCPCP000004_merged.rds"
)

@@

## Compare expression when SingleR and consensus annotations match

>>>>

# Define color ramp for shared use in the heatmaps
heatmap_col_fun <- circlize::colorRamp2(c(0, 1), colors = c("white", "darkslateblue"))
# Set heatmap padding option
ComplexHeatmap::ht_opt(TITLE_PADDING = grid::unit(0.6, "in"))

# settings
options(
  dplyr.summarise.inform = FALSE, 
  readr.show_col_types = FALSE
)
```

@@

# merged SCE file
sce_file <- file.path(
  merged_dir,
  "SCPCP000004_merged.rds"
)

@@

## Gene expression of unclassified consensus cells
